---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MCERA5

<!-- badges: start -->

<!-- badges: end -->

'MCERA5' is designed to simplify the download and analysis of the European Centre for Medium-range Weather Forecasts ReAnalysis 5 (ERA5) family. It simplifies the downloading of ERA5 datasets by summarizing

It uses the European Centre for Medium-Range Weather Forecasts [`ecmwfr` package](https://github.com/bluegreen-labs/ecmwfr) in `R` to interface the ECMWFR API web service and access the ERA5 data from the [Copernicus Climate Data Store (CDS)](https://cds.climate.copernicus.eu/cdsapp#!/home).

## Installation 
'MCERA5' is not yet on CRAN, so it needs to be installed via GitHub. You can install the latest development version of 'MCERA5' like this:

```{r}
remotes::install_github("marlenebauer/MCERA5")
```

Users require a user ID and API key to access the Copernicus Store Data (CDS) API which can be found at their [CDS profile](https://cds.climate.copernicus.eu/user/login).

Additionally, you need to download the 'rgeoboundaries' package from GitHub to exploit the entire capability of 'MCERA5':

```{r}
remotes::install_github("wmgeolab/rgeoboundaries")
library(rgeoboundaries)
```

## Get started

After successfully installed, you can load the package as below and work with the provided functions.


An overview of the ERA5 family datasets with all available dataset_short_names and product_types is provided [here](https://confluence.ecmwf.int/display/CKB/Climate+Data+Store+%28CDS%29+API+Keywords#ClimateDataStore(CDS)APIKeywords-ERA5familydatasets).
A list of all available variables for ERA5-Land can be found [here](https://confluence.ecmwf.int/display/CKB/ERA5-Land%3A+data+documentation) and for ERA5 [here](https://confluence.ecmwf.int/display/CKB/ERA5%3A+data+documentation).

