---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MCERA5

<!-- badges: start -->

<!-- badges: end -->

**MCERA5** is designed to simplify the download and analysis of the European Centre for Medium-range Weather Forecasts ReAnalysis 5 (ERA5) family. It uses the European Centre for Medium-Range Weather Forecasts [`ecmwfr`package](https://github.com/bluegreen-labs/ecmwfr) in `R` to interface the ECMWFR API web service and access the ERA5 data from the [Copernicus Climate Data Store (CDS)](https://cds.climate.copernicus.eu/cdsapp#!/home).


The packages is designed to 
- be user-friendly and provide a simple interface to access the ERA5 data.
- download ERA5 data for a specific time period, variable and area of interest with  several filter options
- perform time-series-analysis of the ERA5 data 
- visualize the ERA5 data and results of the analysis


## Installation

**MCERA5** is not yet on CRAN, so it needs to be installed via GitHub. You can install the latest development version of **MCERA5** like this:

```{r}
remotes::install_github("marlenebauer/MCERA5")
```

Users require a user ID and API key to access the Copernicus Store Data (CDS) via the ECMWFR API which can be found at their [CDS profile](https://cds.climate.copernicus.eu/user/login).

Additionally, you need to download the ´rgeoboundaries` package from GitHub to exploit the entire capability of **MCERA5**:

```{r}
remotes::install_github("wmgeolab/rgeoboundaries")
library(rgeoboundaries)
```

## Get started

After successfully installed, you can load the package as below and work with the provided functions:
```{r}
library(MCERA5)
```


For downloading ERA5 data, call the 'get_era5' function.
By default


```{r, eval = FALSE}
user <- "Your user ID"
key <- " Your personal API key"
dataset_short_name <- "reanalysis-era5-land-monthly-means"
product_type <- "monthly_averaged_reanalysis"
variable <- "2m_temperature"
StartDate <- "2009-12-01"
EndDate <- "2020-02-29"
season <- "DJF"
time = sprintf("%02d:00", 4:5) # c("04:00", "05:00")
country_name <- "Germany" # provided by the 'rgeoboundaries' package
# call the get_era5 function
# optional parameters need to be called as shown below
data <- get_era5(user, key, dataset_short_name, variable, StartDate, EndDate, time, season=season, country_name=country_name, product_type=product_type)
```



```{r, eval = FALSE}
result <- raster_analysis(data)
# Plot the slope of result
result_plot <- monthly_plots(result, "mean", "output_file.png")
```



An overview of the ERA5 family datasets with all available dataset_short_names and product_types is provided [here](https://confluence.ecmwf.int/display/CKB/Climate+Data+Store+%28CDS%29+API+Keywords#ClimateDataStore(CDS)APIKeywords-ERA5familydatasets). A list of all available variables for ERA5-Land can be found [here](https://confluence.ecmwf.int/display/CKB/ERA5-Land%3A+data+documentation) and for ERA5 [here](https://confluence.ecmwf.int/display/CKB/ERA5%3A+data+documentation).
